Temporality is Important for Networks of Hospital Patient Transfers

### 2024-10-30 reports/report.qmd
Add in exponential approximation curves to readmit fig

fig, ax = plt.subplots()
ax.scatter(*(readmit_window.to_numpy().T), marker='.')
ax.set_xscale('asinh') # todo fix xticks
ax.set_yscale('log')
ax.set_xlabel('Readmission Window (days)')
ax.set_ylabel('Count')
ax.set_aspect(0.5)
ax.set_xticks([0, 1, 1e1, 1e2])
ax.set_xticks([2, 5, 2e1, 5e1, 2e2, 5e2], minor=True)
sns.despine()
```

@@

```{python}
#| label: fig-logrank-comparison
#| fig-cap: Log-rank test comparisons between experiments

>>>>

# naive static distribution
mean_window = (
    readmit_window
    .with_columns((pl.col('readmission_time') * pl.col('count')).alias('weighted_sum'))
    .select(pl.col('weighted_sum').sum() / pl.col('count').sum())
    .item()
)
num_readmits = readmit_window.select(pl.col('count').sum()).item()

xs = np.arange(0, 366, dtype=np.float64)
naive_static_dist = num_readmits / mean_window * np.exp(-xs / mean_window) # scaling to N

# piecewise distribution (improved static)
threshold = 4
shorts = readmit_window.filter(pl.col('readmission_time') <= threshold)
longs = readmit_window.filter(pl.col('readmission_time') > threshold)

short_window = (
    shorts
    .with_columns((pl.col('readmission_time') * pl.col('count')).alias('weighted_sum'))
    .select(pl.col('weighted_sum').sum() / pl.col('count').sum())
    .item()
)
n_shorts = shorts.select(pl.col('count').sum()).item()

long_window = (
    longs
    .with_columns((pl.col('readmission_time') * pl.col('count')).alias('weighted_sum'))
    .select(pl.col('weighted_sum').sum() / pl.col('count').sum())
    .item()
)
n_longs = longs.select(pl.col('count').sum()).item()

sxs = np.arange(0, threshold+1, dtype=np.float64)
short_dist = n_shorts / short_window * np.exp(-sxs / short_window)

lxs = np.arange(threshold, 366, dtype=np.float64)
long_dist = n_longs / long_window * np.exp(-lxs / long_window)

fig, ax = plt.subplots()
ax.scatter(*(readmit_window.to_numpy().T), marker='.', color='k')
h_0 = ax.plot(xs, naive_static_dist, color='C0', label='Naïve Static')
h_1 = ax.plot(sxs, short_dist, color='C1', label='Improved Static')
ax.plot(lxs, long_dist, color='C1')
ax.axvline(threshold, color='C1', linestyle='dashed')
ax.set_xscale('asinh')
ax.set_yscale('log')
ax.set_xlabel('Readmission Window (days)')
ax.set_ylabel('Count')
ax.set_aspect(0.5)
ax.set_xticks([0, 1, 1e1, 1e2])
ax.set_xticks([2, 5, 2e1, 5e1, 2e2, 5e2], minor=True)
ax.set_xlim(-1e-1, 1e3) # !! this is manual
ax.set_ylim(5e3, 1e8) # !! this is manual
ax.legend(handles=[*h_0, *h_1])
sns.despine()
```

@@

```{python}
#| label: fig-logrank-comparison
#| fig-cap: Log-rank test comparisons between experiments
#| cache: true
